Forecasting the 2024 U.S. Presidential Election

### 2024-11-03 paper/paper.qmd

## YouGov Pollster Methodology Overview and Evaluation
YouGov conducts online surveys through their proprietary panel of U.S. adults, using nonprobability sampling methods combined with sophisticated weighting procedures to achieve representative results. Their approach balances speed and cost-effectiveness with statistical rigor through careful sample selection and data quality controls.

### Survey Population and Sampling
YouGov's target population typically comprises all U.S. adults or adult citizens, with their sampling frame consisting of their opt-in online panel covering approximately 95% of Americans. For general population surveys, they aim for 1,000-2,000 respondents, selected based on demographic and political characteristics to match the target population.

### Panel Recruitment and Participation
Panel members are recruited through advertising and website partnerships, with surveys offered in multiple languages including Spanish to ensure broad representation. Participants receive points exchangeable for small monetary rewards, though many report being motivated by the desire to contribute to research.

### Quality Control
YouGov employs several measures to maintain data quality:

@@

# Display the transposed table
kable(data_overview)
```

@@

data %>%
  summarise(
    across(c(sample_size, pollscore, numeric_grade, transparency_score),
           list(
             Mean = mean,
             Median = median,
             SD = sd,
             Min = min,
             Max = max
           ), 
           .names = "{.fn}_{.col}",
           na.rm = TRUE)
  ) %>%
  pivot_longer(everything(), 
               names_to = c("Statistic", "Variable"),
               names_sep = "_",
               values_to = "Value") %>%
  pivot_wider(names_from = Variable,
              values_from = Value) %>%
  mutate(across(-Statistic, ~round(.x, 2))) %>%
  kable()
```

@@

data %>%
  ggplot(aes(x = fct_infreq(methodology))) +
  geom_bar() +
  coord_flip() +
  theme_minimal() +
  labs(x = "Methodology",
       y = "Count") +
  theme(axis.text.y = element_text(size = 8))
```

@@

ggplot(data, aes(x = pct, fill = candidate_name)) +
  geom_histogram(bins = 30, position = "identity") +
  facet_wrap(~ candidate_name) +
  labs(x = "Percentage of Support",
       y = "Count") +
  scale_fill_discrete(name = "Candidates") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

@@

data %>%
  count(state) %>%
  arrange(desc(n)) %>%
  rename("State" = state,
         "Number of Polls" = n) %>%
  kable(format = "latex", booktabs = TRUE)
```

@@

data %>%
  mutate(end_date = as.Date(end_date)) %>%
  mutate(week = floor_date(end_date, "week")) %>%
  count(week) %>%
  ggplot(aes(x = week, y = n)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Week",
       y = "Number of Polls") +
  scale_x_date(date_breaks = "2 weeks", date_labels = "%b %d")
```

@@

>>>>

## YouGov Pollster Methodology Overview and Evaluation
YouGov[@YouGov] utilizes an online panel with non-probability sampling, adjusting for demographic imbalances through weighting techniques. This approach ensures that survey results are representative of the broader population, despite the limitations of non-random sampling.

The primary strength of YouGov's methodology lies in its efficiency and cost-effectiveness, enabling rapid data collection. However, the reliance on non-probability sampling can introduce biases, which are partially mitigated by their rigorous weighting process. While effective in providing timely insights, this method requires careful consideration of its limitations in representativeness.

### Survey Population and Sampling
YouGov’s surveys target U.S. adults, utilizing an opt-in online panel that covers approximately 95% of the population. For general population surveys, they typically sample between 1,000 and 2,000 respondents. These participants are selected to reflect key demographic and political characteristics, ensuring the sample is representative of the broader population.

### Panel Recruitment and Participation
YouGov[@YouGov] recruits panel members through targeted advertising and partnerships with various websites. Surveys are available in multiple languages, including Spanish, to ensure inclusivity and broad demographic representation. Participants are incentivized with points redeemable for small monetary rewards, though many join to contribute to research efforts.

### Quality Control
YouGov[@YouGov] employs several measures to maintain data quality:

@@

# Display the transposed table
kable(data_overview)
```
@tbl-overview_data provides an overview of key variables from different polls conducted by various organizations, including Washington Post/George Mason University, CNN/SSRS, Siena/NYT, and YouGov. It highlights differences in methodologies, such as live phone interviews, online panels, and mixed methods, as well as sample sizes ranging from 708 to 1,142 respondents. Pollscores, which reflect pollster reliability, vary from -1.5 (indicating higher reliability for Siena/NYT) to -0.6 (for CNN/SSRS). Transparency scores show that YouGov and CNN/SSRS exhibit full transparency with perfect scores of 10.

The table also includes data on candidate support percentages, with Donald Trump polling between 42% and 48% across various states and Kamala Harris receiving 48% in Michigan. This snapshot reveals the diversity in poll designs, geographical focus, and methodological rigor, which are crucial for understanding the variability in polling data.

@@

data %>%
  summarise(
    across(c(sample_size, pollscore, numeric_grade, transparency_score),
           list(
             Mean = mean,
             Median = median,
             SD = sd,
             Min = min,
             Max = max
           ), 
           .names = "{.fn}_{.col}",
           na.rm = TRUE)
  ) %>%
  pivot_longer(everything(), 
               names_to = c("Statistic", "Variable"),
               names_sep = "_",
               values_to = "Value") %>%
  pivot_wider(names_from = Variable,
              values_from = Value) %>%
  mutate(across(-Statistic, ~round(.x, 2))) %>%
  kable()
```
@tbl-poll-metrics presents the summary statistics for key poll metrics, including sample size, pollscore (pollster reliability), numeric grade, and transparency score. The average sample size across polls is 1,114.76 respondents, with a standard deviation of 583.72, indicating variability in the number of participants. The median sample size is 1,000, with a minimum of 450 and a maximum of 4,253 respondents.

The average pollscore is -1.06, with a median of -1.10, reflecting generally high reliability across pollsters (lower scores indicate greater reliability). The numeric grade, which measures methodological rigor, averages 2.89 with minimal variability (SD of 0.10). The transparency score averages 8.59, suggesting most polls are transparent about their methods, though scores range from 6.00 to 10.00. These statistics highlight the overall quality and variation in polling practices used in the analysis.

@@

data %>%
  ggplot(aes(x = fct_infreq(methodology))) +
  geom_bar() +
  coord_flip() +
  theme_minimal() +
  labs(x = "Methodology",
       y = "Count") +
  theme(axis.text.y = element_text(size = 8))
```
@fig-methodology-dist illustrates the distribution of various polling methodologies used in the dataset. The most frequently employed methods include "Live Phone," "Online Panel," and "Live Phone/Text-to-Web," highlighting a preference for direct communication methods combined with online components. Less common methodologies, such as "Live Phone/Online Panel/Text" and "Live Phone/Email," appear at the lower end of the distribution. This diversity in polling methods reflects the varied approaches taken by pollsters to gather representative data, balancing traditional techniques with modern, web-based options.

@@

ggplot(data, aes(x = pct, fill = candidate_name)) +
  geom_histogram(bins = 30, position = "identity") +
  facet_wrap(~ candidate_name) +
  labs(x = "Percentage of Support",
       y = "Count") +
  scale_fill_discrete(name = "Candidates") +
  theme_minimal() +
  theme(legend.position = "bottom")
```
@fig-candidate-support shows the distribution of support percentages for Donald Trump and Kamala Harris. Both distributions are centered around the mid-40% to mid-50% range, reflecting a competitive race. Trump's support is more concentrated around the 45-50% range, indicating relatively consistent polling results. Harris’s distribution is slightly more varied, suggesting greater fluctuation in her polling support. This visualization highlights the close contest between the two candidates, with neither consistently achieving overwhelming support across polls.

@@

data %>%
  count(state) %>%
  arrange(desc(n)) %>%
  rename("State" = state,
         "Number of Polls" = n) %>%
  kable(format = "latex", booktabs = TRUE)
```
@tbl-state-polls illustrates the number of polls conducted over time, showing weekly fluctuations in polling activity. There is a noticeable increase in the number of polls around mid-September, peaking at over 160 polls in a week, followed by a decline as the election date approaches. This pattern suggests heightened polling activity during key points in the campaign, likely driven by major events or debates, before tapering off closer to the election. The variability highlights how polling frequency can change in response to the evolving political landscape.

@@

data %>%
  mutate(end_date = as.Date(end_date)) %>%
  mutate(week = floor_date(end_date, "week")) %>%
  count(week) %>%
  ggplot(aes(x = week, y = n)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(x = "Week",
       y = "Number of Polls") +
  scale_x_date(date_breaks = "2 weeks", date_labels = "%b %d")
```
@fig-temporal-polling provides the polling frequency by state, highlighting where polling efforts were concentrated. National polls dominate with 261 instances, while key battleground states like Pennsylvania (86 polls), Wisconsin (82 polls), and North Carolina (64 polls) also see significant attention. These states are critical for determining election outcomes, explaining the higher frequency. Conversely, states like Missouri, Montana, and Nebraska show fewer polls (4 each), reflecting less competitive races or a perceived lower impact on the overall election result. This distribution underscores the strategic focus on swing states in polling efforts.

@@

@fig-sample-size shows the distribution of sample sizes across the polls in the dataset. The majority of polls have sample sizes clustered around 1,000 respondents, which is a typical size for achieving a balance between precision and cost. A few polls have significantly larger sample sizes, extending beyond 2,000, with some even exceeding 4,000 respondents. This suggests that while most polls aim for a moderate sample size, there are instances where more extensive sampling is conducted, possibly for greater accuracy or in critical regions. The distribution reflects the common practice of balancing statistical reliability with logistical constraints.
